A robust framework for variable extrusion width concentric toolpath generation

### 2019-07-08 4_method.tex
rewrite grounded medial axis > voronoi quadrangualtion

The medial axis of a polygonal shape is a subset of the voronoi diagram generated on the line segments of the shape. \todo{[citation needed]}

@@

\subsubsection{grounded Medial Axis Transform}
See \cref{gmat}.
The medial axis is commonly defined either as the set of points with more than one closest point on the boundary or as the set of quench sites of a fire started at the outline polygon growing inward.
A novel way of conceptualizing the medial axis is as a data structure which encodes the distance field.
The medial axis is the set of all points where the derivative of the distance field is discontinuous.

The medial axis transform (MAT) is the combination of the medial axis with at each node the distance values $R$.

We propose a modified MAT: the grounded medial axis transform: gMAT.
The distance field defined by the gMAT approximates the distance field of the MAT using \uwave{piece-wise linear quads}.
The gMAT is the set of all points where the derivative of the distance field is not constant.

Each node in the gMAT is connected to the outline via a \emph{single} bone.
This condition is violated on a MAT where there are concave outline verts.
The gMAT segments the polygon in quads consisting of 1 outline segment and 3 bones, one of which is not directly connected to the outline.
For concave verts the outline segments is missing and the quad becomes a triangle;
likewise for convex sections it may happen that the inner bone is missing from the quad so that it forms a triangle.

For a normal MAT it is already the case that
for a bone segment $v_0 v_1$ generated by two outline segments $p_0 p_1$ and $p_2 p_3$,
the distance on locations along $v_0 v_1$ can be interpolated linearly between $R(v_0)$ and $R(v_1)$.
The distance field between $v_0 v_1$ and $p_0 p_1$ can be constructed linearly as well.

For a MAT the same does not hold for parabolic bones or bones generated by two concave outline verts.
We therefore discretize these segments and connect the introduced nodes to the oulines using new ribs.
The resulting quads encode the original distance field in a piece-wise fashion using linear gradients.

The MAT is a subset of the Voronoi diagram inside the part, which in turn is a subset of the gMAT.
See \cref{voronoi_MAT}.

>>>>

@@

\subsubsection{Voronoi Quadrangulation}
The medial axis of a polygonal shape can be obtained from the Voronoi Diagram (VD) generated on the line segments and vertices of the shape. \cite{lee1982medial}
First we throw away all locations in the Voronoi diagram which fall outside the boundary shape.
We can then obtain the medial axis by further reducing the Voronoi bones connected to a concave corner in the boundary shape.

However, instead of removing bones from the Voronoi diagram we will introduce more bones such that the skeleton discretizes the boundary shape into quads within which the $R$ can be interpolated linearly.
We call the resulting skeletonization the \emph{Voronoi Quadrangulation} (VQ).
The VQ greatly simplifies the processing required downstream in our framework.

In order to generate the VQ, we start by generating a normal Voronoi Diagram and remove all segments which lie outside of the boundary shape.
We then introduce bones such that each node in the VQ is directly connected to the outline via a single bone:
each node in the VQ is connected to the closest points on the boundary (its \emph{support}).
As such the VQ divides the polygon in quads consisting of 1 outline segment and 3 bones, one of which is not directly connected to the outline.
For concave verts the quad is missing the outline segments and so it regresses into a triangle;
likewise for convex sections it may happen that the inner bone is missing from the quad so that it forms a triangle.
\todo{TODO: make pics}

We then also discretize parabolic bones and bones generated by two concave outline vertices into approximately equidistant segments.
That way we can approximate the feature radius $R$ in between two nodes $v_0$ and $v_1$ in the VQ by interpolating linearly between $R(v_0)$ and $R(v_1)$.
Furthermore, we can linearly interpolate the distance field of a quad $p_0v_0v_1p_1$ (where $p_0$ and $p_1$ lie on the outline shape):
For a point $a \in p_0v_0$ and a point $b \in p_1v_1$ for which $R(a) = R(b)$ we have that all points in the line segment $ab$ have the same feature radius $R$.

i
